Efficient implementation of kernel filtering

### 2007-07-03 article/Article.tex
add a few images, to illustrate the paper
darcs-hash:20070703140234-2fc9d-ba80dd3cb0c7125057a6f4d80f77232b89222323.gz

The morphology filters utilize a new class -- {\em
FlatStructuringElement} to describe, arbitary and decomposable
structuring elements. It provides the following methods to create
structuring elements with different characteristics:
\begin{itemize}
  \item \verb$Ball()$ generate a ball structuring element (a circle in 2D). It takes the 
	radius of the structuring element as parameter.
  \item \verb$Box()$ produces a box structuring element. It takes the radius 
	of the structuring element as parameter.
  \item \verb$Poly()$ produces an approximation to a circle or sphere using 
	line structuring elements, taking the desired radius and number of 
	lines as parameters. In the 3D case an approximation of a sphere will 
	be attempted. Caution is advised because this is not well tested yet.
  \item \verb$FromImage()$ produces a structuring element from an image. The image is passed
as parameter to the method. A optional parameter can also be passed: the pixel value
to be considered as the foreground value in the image. This value defaults to
\verb$NumericTraits< PixelType >::max()$. This lets the user visualize the structuring element.
\end{itemize}

The algorithm used by a filter is set by the {\em SetAlgorithm}
method, with options of {\em BASIC}, {\em HISTO}, {\em VHGW} and {\em
ANCHOR}, for the traditional ITK implementation, the moving histogram
algorithm, the van Herk, Gil, Werman algorithm and the anchor
algorithm respectively. The VHGW and ANCHOR algorithms can only be
used for Box and Poly structuring elements. VHGW is more thoroughly
tested. The HISTO algorithm produces the identical results to BASIC,
and is always faster. It is the default and should be used if you need
precisely defined, non rectangular, structuring elements. If a Box
structuring element is needed then VHGW or ANCHOR should be used, as
they offer the best performance and are exact in that case. Poly
structuring elements are approximations of circles that will offer
improved performance with VHGW or ANCHOR algorithms, but the user will
need to consider whether the approximation is suitable for the
application in question.

@@

\begin{figure}[htbp]
\begin{center}
\subfigure[Mean]{\includegraphics[scale=0.62]{fastRankMean-perfMean}}
\subfigure[Median]{\includegraphics[scale=0.62]{fastRankMean-perfMedian}}
\caption{Execution times for several algorithms of mean filters (a) and
median filters (b).\label{fig:perfRank}
Results are reported in Tables \ref{tab:perfRankMean} and  \ref{tab:perfRankMedian}.}
\end{center}
\end{figure}

>>>>

The morphology filters utilize a new class -- {\em
FlatStructuringElement} to describe, arbitary and decomposable
structuring elements. It provides the following methods to create
structuring elements with different characteristics:
\begin{itemize}
  \item \verb$Ball()$ generate a ball structuring element. It takes the 
	radius of the structuring element as parameter.
  \item \verb$Box()$ produces a box structuring element. It takes the radius 
	of the structuring element as parameter.
  \item \verb$Poly()$ produces an approximation to a circle or sphere using 
	line structuring elements, taking the desired radius and number of 
	lines as parameters. In the 3D case an approximation of a sphere will 
	be attempted. Caution is advised because this is not well tested yet.
  \item \verb$FromImage()$ produces a structuring element from an image. The image is passed
as parameter to the method. A optional parameter can also be passed: the pixel value
to be considered as the foreground value in the image. This value defaults to
\verb$NumericTraits< PixelType >::max()$. This lets the user visualize the structuring element.
\end{itemize}

The algorithm used by a filter is set by the {\em SetAlgorithm}
method, with options of {\em BASIC}, {\em HISTO}, {\em VHGW} and {\em
ANCHOR}, for the traditional ITK implementation, the moving histogram
algorithm, the van Herk, Gil, Werman algorithm and the anchor
algorithm respectively. The VHGW and ANCHOR algorithms can only be
used for Box and Poly structuring elements. VHGW is more thoroughly
tested. This HISTO algorithm produces the identical results to BASIC,
and is always faster. It is the default and should be used if you need
precisely defined, non rectangular, structuring elements. If a Box
structuring element is needed then VHGW or ANCHOR should be used, as
they offer the best performance and are exact in that case. Poly
structuring elements are approximations of circles that will offer
improved performance with VHGW or ANCHOR algorithms, but the user will
need to consider whether the approximation is suitable for the
application in question.

@@

\begin{figure}[htbp]
\begin{center}
\subfigure[Mean]{\includegraphics[scale=0.62]{fastRankMean-perfMean}}
\subfigure[Median]{\includegraphics[scale=0.62]{fastRankMean-perfMedian}}
\caption{Execution times for several algorithms of mean filters (a) and
median filters (b).\label{fig:perfRank}}
\end{center}
\end{figure}
